Automated Dynamic Slice Backsolving

### 2014-03-23 docs/paper/fsuthesis/thesis-template/paper.tex
read over hard copy and made some changes

Finding software bugs is a difficult but lucrative endeavour, and fuzzing is one technique often employed for finding bugs, particularly exploitable vulnerabilities. However, when no source code is available, fuzzing complex programs effectively can prove difficult, and as techniques become more sophisticated they require more resources and time. We present a technique, automated dynamic slice backsolving, which, to the best of our knowledge, represents a novel way to improve fuzzers' code coverage, without resorting to heavyweight techniques like symbolic execution. We demonstrate this technique with a proof of concept fuzzer which explores paths in a binary to effectively reveal a secret, performing an oracle attack without an oracle. Our approach requires no source code, no manual instrumentation, and no symbolic execution, and, as our results show, can reliably discover and explore new execution paths in a timely fashion. We believe dynamic slice backsolving represents a potentially strong complementary technique for modern fuzzers to implement.

@@

Because of the high market value of finding bugs, either to patch or exploit, many researchers create their own fuzzers, or use open source products like Peach [Z]. These fuzzers vary in purpose and sophistication. The simplest of fuzzers may have little understanding of the program it intends to fuzz, merely changing random bytes in user input and monitoring for interesting situations which suggest a bug has been found, such as segmentation faults. A log is produced, which can be analyzed by a programmer at a later date to try and identify the source of the crash. However, fuzzers of this variety, while adept at causing program crashes, tend to find shallow bugs or exit conditions. This is because, with no understanding of the inner workings of a program, a fuzzer is likely to fail checks at the start of a program over and over again [T]. As an example, fuzzing an application which implements HTML by mutating random input bytes will have to reproduce the complex markup tags required to produce valid HTML. It will expend valuable time and resources failing to create valid head and body tags, instead of finding deep bugs.

In order to fuzz more smartly, researchers employ several techniques, two of which are significant for this paper. Dynamic Taint Analysis, or DTA, provides valuable information for guided fuzzing. DTA is a form of dynamic analysis, which marks user input as tainted at some level of granularity, and follows this taint as it propagates through the binary. Certain, task-dependent sinks are identified, and if taint flows to one of these sinks, a trace of program execution allows analysis to follow how taint sources are linked to these sinks. Symbolic execution first runs a program concretely to gather constraints on a particular element, then executes the program symbolically, giving these constraints over to some kind of solver which decides what values the element should given the recorded conditions. Symbolic execution improves code coverage, helping to guide fuzzers into deeper, more interesting parts of a program. Symbolic execution, however, is computationally expensive, with naive implementations running in time exponential to the number of branches [C], which leaves room for refinement by using the technique more wisely or modifying it. Our technique uses DTA to hopefully achieve greater code coverage than random testing, without having to convert code to an intermediate representation or outsource constraints to a solver like symbolic execution.

@@

\begin{itemize}
	\item Requires source code access
	\item Requires programmers to instrument code manually
	\item Must convert code to an intermediate representation
	\item Must emulate the IR in a virtual machine
	\item Outsources constraint solving to heavyweight SMT solvers
\end{itemize}

Because of these downsides, much research tries to attain more reasonable performance by using symbolic execution less or more wisely [J]. We focus instead on approximating symbolic execution's code coverage by using dynamic taint analysis to drive test case mutation. As the native program executes, we dynamically instrument the binary and record execution slices. Memory accesses, loads and stores, and transformations of tainted bytes are recorded, and then used to backsolved to give exact byte values and locations to explore in future runs. Our implementation of this technique requires no source code, no modification to a binary, no conversion to an IR, and no SMT solvers.

@@

Our technique, automated dynamic slice backsolving, uses dynamic taint analysis to watch user input. As user input is introduced, each byte is tracked separately and, when the program transforms or manipulates user input, those transformations are recorded. When branches which depend upon user input are reached, the recorded transformations, if possible, are reversed, backsolving for a new value of a particular byte in user input which will lead execution down a different path in the binary. After execution finishes, input test cases are mutated to reflect this new information, and a new execution test runs.

@@

We have implemented this technique in a proof of concept fuzzer, stubble, which operates on x86 binaries. Stubble dynamically instruments binaries, and automatically generates test files which exercise new paths in the input program. Program input, output, and interesting conditions like segfaults are recorded during execution, and taint propagation is recorded from user input sources to branch sinks. When a tainted branch is found, stubble automically backsolves the execution slice and generates a new test case which will drive the program down the opposite path explored in the current execution.

To test stubble's ability to dynamically discover new branches and generate test cases which will drive future runs down these new branches, we have designed several binaries which receive user input in the form of a file. These binaries open and read the file, comparing a subset of the file contents against a secret. If the file contains the secret, then a win condition is printed, otherwise a lose condition is printed. For the proof of concept, this win condition could be thought of as a segfault, or other interesting condition that suggests an exploitable condition exists. We show that stubble is able to discover all paths in the binary, particularly the interesting paths involving the win condition, without any prior knowledge of the secret. Stubble works similarly to an oracle attack, able to discover one character within the secret per run, and preserve work across runs to crack the secret in O(n) tests, where n is the secret length in characters. In contrast, random byte fuzzers, which exhaustively test all user input bytes which their model declares valid, run indefinitely and have no guarantee of discovering the win condition. We have also parallelized stubble at the process level, allowing for an arbitrary number of independent bytes to be reasoned about concurrently. We believe automated dynamic slice backsolving is a reasonable complementary technique to dynamic taint analysis and symbolic execution for binary fuzzing, and that stubble provides a valuable proof of concept for future research into smart fuzzers.

@@

We have developed a technique which, to the best of our knowledge, provides similar code coverage to symbolic execution by using dynamic taint analysis to record relevant program slices and drive test case mutation. As a program runs, the introduction and propagation of taint is recorded. Should taint flow to a sink of interest, the recorded slice is backsolved to find new byte values which will hopefully lead future program runs down new paths. Taint is generally introduced to the program by user input. This can come in the form of user-provided files, command line arguments, or stdin. When user input is detected, it is marked as tainted at the byte level. This means that if user input is conceptualized as a stream of bytes $b_0,b_1,...,b_n$, then the first byte is considered separate from the separate byte, and each is individually followed throughout program execution. This level of granularity introduces significantly more overhead than binary tainting, which marks bytes as either tainted or not tainted, but provides far greater detail into which bytes of user input affect which parts of a program.

Once user input is captured and marked tainted, any memory accesses, loads and stores, and transformations of tainted bytes are recorded as they are encountered. This creates a slice of moves and alterations to the bytes, which can be followed like a trail of breadcrumbs back to the original position of the byte. This continues as the program executes until a conditional branch is reached. When a conditional branch instruction is reached, it is either taken or not taken, based upon the value of some comparison. If this branch depends upon tainted values, which have descended in one way or another from user input, then there is a strong possibility that the "road not taken" could be explored if only user input looked appropriate. In the case where any transformations to user input are reversible, we can backsolve these transformations and, based upon the comparison, modify the byte value so that it leads to the complement of the previous branch condition. Not only this, we can identify which byte $b_0,b_1,...,b_n$ to modify, since we have followed each byte from their introduction. Using this information, we can mutate the previous test case to create a new test which will result in very similar program behavior, with the exception of branching where before it did not branch, and vice versa.

@@

The idea for this technique is raised in [A], which suggests using dynamic taint analysis to identify "hot bytes" of user input, which affect important things in a program, and also to generate backward slices [AA]. Hot bytes become the target of fuzzing, with backward slices providing valuable context to analysts. Our contribution is the realization of this idea for a subset of cases, and the automation of solving these slices. Our hope is that by solving these slices automatically, we can identify not only the exact location but also the exact value of hot bytes.

@@

% x86 example
\begin{lstlisting}[style=asmstyle]
call read					;instrument read syscall
mov eax, [ebp - val]		;taint propagates from val to eax reg
inc eax						;transform eax
mul eax, 5					;transform eax
cmp eax, 42					;cmp and jmp based on tainted reg value
jnz 0x8BADC0DE
\end{lstlisting}

If we already had a test case where the value read onto the stack, after the transformations, did not equal 42, then the cmp instruction would not set the zero flag, and we would jump to the memory location 0xBADC0DE. With dynamic taint analysis in place, we see taint introduced with the read syscall, then moved into the eax register (which is subsequently tainted). After an arbitrary number of transformations, perhaps zero, to the value in the eax register, comes a compare instruction, which checks eax's value against an immediate value. Then we can keep track of specific taint sources, and can record any movements or transformations, we have all the necessary information to "solve" the branch. Once we reach the tainted branch, we know that user input can affect whether we jump or not, and consequently we can backsolve to find out how to affect the branch instruction. In particular, we know the conditional jump instruction jnz depends on the Z flag in the EFLAGS register. We record whatever instruction last modified each flag in EFLAGS, so we handle the compare instruction next. Because we have kept track of taint propagation, we know we can affect the value of eax, but not 42, since it is an immediate value, so we know we need to make the value in eax equal 42. We follow the instructions that have modified the value of eax and use any appropriate operands involved with the inverse operation of the one originally performed on the value to reverse the transformations to eax's value. Finally, we notice eax originally received taint when a value was moved from memory, which was read into memory using the read syscall.

FROM INTRO
We have implemented this technique in a proof of concept fuzzer, stubble, which operates on x86 binaries. Stubble dynamically instruments binaries, and automatically generates test files which exercise new paths in the input program. Program input, output, and interesting conditions like segfaults are recorded during execution, and taint propagation is recorded from user input sources to branch sinks. When a tainted branch is found, stubble automically backsolves the execution slice and generates a new test case which will drive the program down the opposite path explored in the current execution. Stubble is able to reason about large amounts of bytes of user input, for instance by performing oracle attacks on binaries which check user input against large secrets, requiring O(n) test cases to solve the secret with no previous information, where n is the length of the secret. Stubble has also been parallized at the process level, allowing for an arbitrary number of independent bytes to be reasoned about concurrently. We believe automated dynamic slice backsolving is a reasonable complementary technique to dynamic taint analysis and symbolic execution for binary fuzzing.
END FROM INTRO

@@

%The fuzzer currently records implicit and explicit taint flows between memory and registers. When the EFLAGS register is modified, it is checked whether a comparison instruction with tainted operands was the modifier, and if so this is also recorded.

%We also assume the presence of an algorithm which will detect an exploitable condition, provided it is given the proper binary and input to the binary, and an initial test case. The program concretely executes the binary once with the initial test case, recording taint propagation during execution. Stdin, stdout, and stderr are recorded for each run, for later analysis. After the initial run, the program automatically starts solving each byte by backsolving to try and find new paths.

@@

We assume ASLR is disabled for the binary to be fuzzed. This allows the program to easily track and compare execution paths. We have implemented the technique for the x86-32 architecture, because Intel Pin works on a select few architectures, of which x86 is the most prevalent. Since x86 is quite widespread, and vulnerabilities resulting from unsafe C code should persist across binaries, regardless of both the size and flavor of architecture (32 vs. 64-bit, ARM vs. x86 vs. PowerPC etc.), this should be no issue. Compilers try to adhere to the C standard and vulnerabilities like buffer overflows exist at a C source code level.

Fuzzers require intuitive but powerful test harnesses, so that users can easily control how a binary is fuzzed and understand the results of fuzz testing. Currently, stubble records input, output, taint for each test executed, appending an auto-incrementing id to log files and separating results at the directory level. Stubble also keeps track of the mutations which have already been explored. Users can grep for interesting conditions like segfaults or unexpected output, then cross reference the test number with the observed taint flow, input file, and particular mutation tested.

@@

As a proof of concept, stubble lacks the featurefulness of a complete fuzzer. In particular, understanding more diverse types of user input, such as command line arguments, would prove valuable.

@@

@@

MyPinToolMultiProcess, why process level instead of threads, etc.

@@

This bears a strong resemblance to the classic oracle attack in cryptography. Note, however, that stubble would be unable to reason effectively about cryptographic hashes or encryption because of properties like one-way functions and the avalanche effect.

In a traditional oracle attack, the adversary can derive a secret by testing one character at a time. This means an attacker can expect success within $\frac{mn}{2}$ tries on average, where m is the number of character possiblities and n is the length of the secret. Dumb fuzzers, which are unable to reason about the execution paths in a binary, do much worse by mutating random bytes and hoping to hit upon the secret by chance. This strategy can expect success within $\frac{m^n}{2}$ tries on average, since m-many possibilities must be tested for each byte in the secret independently. Stubble performs similarly to an attacker with access to an oracle, although because execution slices are backsolved its time complexity has a smaller constant than $\frac{m}{2}$. Expected number of tries is linear with secret length, as with an oracle attack, but stubble requires roughly two tries per byte, instead of having to test for all possible m.

@@

%
%Currently have results for crackmes, give idea of our fuzzer vs. %peach fuzz, and where i plan to go.

@@

% New types of user input like command line arguments. Can get at argv by passing it directly to driver?

>>>>

Finding software bugs is a difficult but lucrative endeavour, and fuzzing is one technique often employed for finding bugs, particularly exploitable vulnerabilities. However, when no source code is available, fuzzing complex programs effectively can prove difficult, and as techniques become more sophisticated they require more resources and time. We present a technique, automated dynamic slice backsolving, which, to the best of our knowledge, represents a novel way to improve fuzzers' code coverage, without resorting to heavyweight techniques like symbolic execution. We demonstrate this technique with a proof of concept fuzzer which explores paths in a binary to effectively reveal a secret, performing an oracle attack without an oracle. Our approach requires no source code, no manual instrumentation, and no symbolic execution, and, as our results show, can reliably discover and explore new execution paths in a timely fashion. We believe dynamic slice backsolving represents a potentially strong complementary technique for modern fuzzers to implement. In addition, we plan to release and continue development on Stubble's DTA framework, since we not aware of many freely available and active projects.

@@

Because of the high market value of finding bugs, either to patch or exploit, many researchers create their own fuzzers, or use open source products like Peach [Z]. These fuzzers vary in purpose and sophistication. The simplest of fuzzers may have little or no understanding of the program it intends to fuzz, merely changing random bytes in user input and monitoring for interesting situations which hint at bugs, such as segmentation faults. A log is produced, which can be analyzed by a programmer at a later date to try and identify the source of the crash. However, fuzzers of this variety, while adept at causing program crashes, tend to find shallow bugs or exit conditions. This is because, with no understanding of the inner workings of a program, a fuzzer is likely to fail checks at the start of a program over and over again [T]. As an example, fuzzing an application which implements HTML by mutating random input bytes will have to reproduce the complex markup tags required to produce valid HTML. It will expend valuable time and resources failing to create valid head and body tags, instead of finding deep bugs.

In order to fuzz more smartly, researchers employ several techniques, two of which are significant for this paper. Dynamic taint analysis, or DTA, provides valuable information for guided fuzzing. DTA is a form of dynamic analysis, which marks user input as tainted at some level of granularity, and follows this taint as it propagates through the binary. Certain, task-dependent sinks are identified, and if taint flows to one of these sinks, a trace of program execution allows analysts to follow how taint sources are linked to these sinks. Symbolic execution first runs a program concretely to gather constraints on a particular element, then executes the program symbolically, giving these constraints over to some kind of constraint solver which decides what values the element should given the recorded conditions. Symbolic execution improves code coverage, helping to guide fuzzers into deeper, more interesting parts of a program. Symbolic execution, however, is computationally expensive, with naive implementations running in time exponential to the number of branches [C], and often requires source code availability and modification, which leaves room for refinement. Our technique uses DTA to hopefully achieve greater code coverage than random testing, without having to convert code to an intermediate representation or outsource constraints to a solver like symbolic execution.

@@

\begin{itemize}
	\item Requires source code access
	\item Requires programmers to instrument code manually
	\item Must convert code to an intermediate representation
	\item Outsources constraint solving to heavyweight satisfiability solvers
\end{itemize}

Because of these downsides, much research tries to attain more reasonable performance by using symbolic execution less or more wisely [J]. We focus instead on approximating symbolic execution's code coverage by using dynamic taint analysis to drive test case mutation. As the native program executes, we dynamically instrument the binary and record execution slices. Memory accesses, loads and stores, and transformations of tainted bytes are recorded, and then used to backsolve to give exact byte values and locations to explore in future runs. Our implementation of this technique requires no source code, no modification to a binary, no conversion to an IR, and no SMT solvers.

@@

Our technique, automated dynamic slice backsolving, uses dynamic taint analysis to watch user input. As user input is introduced, each byte is tracked separately and, when the program transforms, uses, or moves user input, those actions are recorded. When branches which depend upon user input are reached, the recorded slice, if possible, are reversed, backsolving for a new value of a particular byte in user input which will lead execution down a different path in the binary. After execution finishes, input test cases are mutated to reflect this new information, and a new execution test runs.

@@

We have implemented this technique in a proof of concept fuzzer, Stubble, which operates on x86 programs. Stubble dynamically instruments binaries, and automatically generates test files which exercise new paths in the input program. Program input, output, and interesting conditions like segfaults are recorded during execution, and taint propagation is recorded from user input sources to branch sinks. When a tainted branch is found, stubble automically backsolves the execution slice and generates a new test case which will drive the program down the opposite path explored in the current execution.

To test Stubble's ability to dynamically discover new branches and generate test cases which will drive future runs down these new branches, we have designed several binaries which receive user input in the form of a file. These binaries open and read the file, comparing a subset of the file contents against a secret. If the file contains the secret, then a win condition is printed, otherwise a lose condition is printed. For the proof of concept, this win condition could be thought of as a segfault, or other interesting condition that suggests an exploitable condition exists. We show that stubble is able to discover all paths in the binary, particularly the interesting paths involving the win condition, without any prior knowledge of the secret. Stubble works similarly to an oracle attack, able to discover one character within the secret per run, and preserve work across runs to crack the secret in O(n) tests, where n is the secret length in characters. In contrast, random byte fuzzers, which exhaustively test all user input bytes which their model declares valid, run indefinitely and have no guarantee of discovering the win condition. We also present a key observation for improving path exploration in the x86 architecture, namely the finite number of conditional branch statements and instructions which modify the flags which branch statements use. Targetting these instructions specifically pays dividends. Lastly, we have also parallelized Stubble at the process level, allowing for an arbitrary number of independent bytes to be reasoned about concurrently. We believe automated dynamic slice backsolving is a reasonable complementary technique to dynamic taint analysis and symbolic execution for binary fuzzing, and that stubble provides a valuable proof of concept for future research into smart fuzzers.

@@

We have developed a technique which, to the best of our knowledge, provides similar code coverage to symbolic execution by using dynamic taint analysis to record relevant program slices and drive test case mutation. As a program runs, the introduction and propagation of taint is recorded. Should taint flow to a sink of interest, the recorded slice is backsolved to find new byte values which will hopefully lead future program runs down new paths. Taint is generally introduced to the program by user input. This can come in the form of user-provided files, command line arguments, or stdin. When user input is detected, it is marked as tainted at the byte level. This means that if user input is conceptualized as a stream of bytes $b_0,b_1,...,b_n$, then the first byte is considered separate from the second byte and so on, with each byte individually followed throughout program execution. This level of granularity introduces significantly more overhead than binary tainting, which marks bytes as either tainted or not tainted, but provides far greater detail into which bytes of user input affect which parts of a program.

Once user input is captured and marked tainted, any memory accesses, loads and stores, and transformations of tainted bytes are recorded as they are encountered. This creates a slice of operations involving the tainted bytes, which can be followed like a trail of breadcrumbs back to the original position of the byte. This continues as the program executes until a conditional branch is reached. When a conditional branch instruction is reached, it is either taken or not taken, based upon the value of some comparison. If the branch condition depends upon tainted values, which have descended in one way or another from user input, then there is a strong possibility that the "road not taken" could be explored if only user input looked appropriate. In the case where all transformations to user input are reversible, we can backsolve these transformations and, based upon the comparison, modify the byte value so that it leads to the complement of the previous branch condition. Not only this, we can identify which byte $b_0,b_1,...,b_n$ to modify, since we have followed each byte from their introduction. Using this information, we can mutate the previous test case to create a new test which will result in very similar program behavior, with the exception of branching where before it did not branch, and vice versa.

@@

The idea for this technique is raised in [A], which suggests using dynamic taint analysis to identify "hot bytes" of user input, which affect important things in a program, and also to generate backward slices [AA]. Hot bytes become the target of fuzzing, with backward slices providing valuable context to analysts. Our contribution is the realization of this idea for a subset of cases, and the automation of solving these slices. Our hope is that by solving these slices automatically, we can identify not only the exact location but also the relevant values of hot bytes.

@@

% x86 example
\begin{lstlisting}[style=asmstyle]
call read					;instrument read syscall
mov eax, [ebp - val]	        ;taint propagates from val to eax reg
inc eax						;transform eax
mul eax, 7					;transform eax
cmp eax, 42					;cmp and jmp based on tainted reg value
jnz 0x8BADC0DE
\end{lstlisting}

If we already had a test case where the value read onto the stack, after the transformations, did not equal 42, then the cmp instruction would not set the zero flag, or ZF, and we would jump to the memory location 0xBADC0DE. With dynamic taint analysis in place, we see taint introduced with the read syscall, then moved into the eax register (which is subsequently tainted). After an arbitrary number of transformations, perhaps zero, to the value in the eax register, comes a compare instruction, which checks eax's value against an immediate value. Then we can keep track of specific taint sources, and can record any movements or transformations, we have all the necessary information to "solve" the branch. Once we reach the tainted branch, we know that user input can affect whether we jump or not, and consequently we can backsolve to find out how to affect the branch instruction. In particular, we know the conditional jump instruction jnz depends on the Z flag in the EFLAGS register. We record whatever instruction last modified each flag in EFLAGS, so we handle the compare instruction next. Because we have kept track of taint propagation, we know we can affect the value of eax, but not 42, since it is an immediate value, so we know we need to make the value in eax equal 42. We follow the instructions that have modified the value of eax and use any appropriate operands involved with the inverse operation of the one originally performed on the value to reverse the transformations to eax's value. Finally, we notice eax originally received taint when a value was moved from memory, which was read into memory using the read syscall.

We have implemented this technique in a proof of concept fuzzer, Stubble, which operates on x86 binaries. Stubble dynamically instruments binaries, and automatically generates test files which exercise new paths in the input program. Program input, output, and interesting conditions like segfaults are recorded during execution, and taint propagation is recorded from user input sources to branch sinks. When a tainted branch is found, Stubble automically backsolves the execution slice and generates a new test case which will drive the program down the opposite path of that explored in the current execution. Stubble is able to reason about large amounts of bytes of user input, for instance by performing oracle attacks on binaries which check user input against large secrets, requiring O(n) test cases to solve the secret with no previous information, where n is the length of the secret. Stubble has also been parallized at the process level, allowing for an arbitrary number of independent bytes to be reasoned about concurrently.

@@

This is made possible by a key observation about the x86 architecture. There are a finite number of conditional branch instructions, which branch based upon the value of one or a combination of flags located in the EFLAGS register. In particular, the carry, overflow, parity, sign, and zero flags (CF, OF, PF, SF, ZF) are used to determine whether or not to branch. For example, the je, or jump if equal, instruction branches when the zero flag is set, while the jg, or jump if greater than, instruction branches when the zero flag is unset and the sign and overflow flags are equal. There are also a limited number of instructions which modify these five flags, and some instructions modify these flags unconditionally, but always setting, unsetting, or toggling them. Thus, we can monitor these flags in the EFLAGS register, and only must take note of the last tainted instruction that modified these flags, since untainted instructions cannot be controlled by user input and overwritten taint instructions cannot effect the branch instructions. This introduces little additional overhead, since we already must monitor each instruction executed to watch for track taint.

@@

We assume ASLR is disabled for the binary to be fuzzed. This allows the program to easily track and compare execution paths. We have implemented the technique for the x86-32 architecture, because Intel Pin works on a few select architectures, of which x86 is the most prevalent. Since x86 is quite widespread, and vulnerabilities resulting from unsafe C code should persist across binaries, regardless of both the size and flavor of architecture (32 vs. 64-bit, ARM vs. x86 vs. PowerPC etc.), this should be no issue. Compilers try to adhere to the C standard and vulnerabilities like buffer overflows exist at a C source code level.

We also assume the presence of an algorithm which will detect an exploitable condition, provided it is given the proper binary and input to the binary, and an initial test case. For detecting real exploits, something like monitoring when tainted values overwrite the EIP register would be valuable. For the proof of concept we use a win condition hard coded into the input binary.

Fuzzers require intuitive but powerful test harnesses, so that users can easily control how a binary is fuzzed and understand the results of fuzz testing. Currently, stubble records input, output, and taint explored for each test executed, appending an auto-incrementing id to log files and separating results at the directory level. Stubble also keeps track of the mutations which have already been explored. Users can grep for interesting conditions like segfaults or unexpected output, then cross reference the test number with the observed taint flow, input file, and particular mutation tested.

@@

As a proof of concept, stubble lacks the featurefulness of a complete fuzzer. In particular, understanding more diverse types of user input, such as command line arguments, would prove valuable. Stubble currently only instruments the read syscall. When an appropriate input file is opened it marks all bytes read as tainted. A more featurefull fuzzer would instrument other system calls which could introduce taint, and would also handle C library functions which are the source of vulnerabilities, like unsafe string copying functions.

@@

TODO we assume away shitty loops

@@

TODO MyPinToolMultiProcess, why process level instead of threads, etc.

@@

This bears a strong resemblance to the classic oracle attack in cryptography. Note as mentioned above, that stubble would be unable to reason effectively about cryptographic hashes or encryption because of properties like one-way functions and the avalanche effect.

In a traditional oracle attack, the adversary can derive a secret by testing one character at a time. This means an attacker can expect success within $\frac{mn}{2}$ tries on average, where m is the number of character possiblities and n is the length of the secret. Dumb fuzzers, which are unable to reason about the execution paths in a binary, do much worse by mutating random bytes and hoping to hit upon the secret by chance. This strategy can expect success within $\frac{m^n}{2}$ tries on average, since m-many possibilities must be tested for each byte in the secret independently. Stubble performs similarly to an attacker with access to an oracle, although because execution slices are backsolved its time complexity has a smaller constant than $\frac{m}{2}$. The expected number of tries is linear with secret length, as with an oracle attack, but stubble requires roughly two tries per byte, instead of having to test for all possible m.

@@

@@

TODO instrument C library routines like strcpy and strcmp.
% New types of user input like command line arguments. Can get at argv by passing it directly to driver?
